Scikit-learn: API design for machine learning

### 2013-06-20 paper.tex
remove figures (no snippet is broken on 2 pages)

Some unsupervised learning
estimators may also implement the \texttt{predict} interface.
The code in Figure~\ref{kmeans-predict} fits a $k$-means model with $k=10$
on training data \texttt{X\_train},
then uses the model's \texttt{predict} method
to obtain cluster labels (integer indices) for unseen data \texttt{X\_test}.

\begin{figure}[h]
\begin{pythoncode}
km = KMeans(n_clusters=10)
km.fit(X_train)
clust_pred = km.predict(X_test)
\end{pythoncode}
\caption{Finding closest centroids for unseen data after $k$-means clustering.}
\label{kmeans-predict}
\end{figure}

@@

\texttt{Pipeline} and \texttt{FeatureUnion} can be
combined to create complex and nested workflows.
Figure~\ref{union+pipeline} illustrates how to create a complex estimator
that computes both linear PCA and kernel PCA features on \texttt{X\_train}
(through a \texttt{FeatureUnion}),
selects the 10 best features in the combination according to an ANOVA test
and feeds those to an $\ell_2$-regularized logistic regression model.

\begin{figure}[h]
\begin{pythoncode}
fu = FeatureUnion([("pca", PCA()),
                   ("kpca", KernelPCA(kernel="rbf"))])

Pipeline([("feat_union", fu),
          ("feat_sel", SelectKBest(k=10)),
          ("log_reg", LogisticRegression(penalty="l2"))
]).fit(X_train, y_train).predict(X_test)
\end{pythoncode}
\caption{Combined use of \texttt{Pipeline} and \texttt{FeatureUnion}.}
\label{union+pipeline}
\end{figure}

>>>>

Some unsupervised learning estimators may also implement the \texttt{predict}
interface. The code in the snippet below fits a $k$-means model with $k=10$ on
training data \texttt{X\_train}, and then uses the  \texttt{predict} method to
obtain cluster labels (integer indices) for unseen data \texttt{X\_test}.
\begin{pythoncode}
km = KMeans(n_clusters=10)
km.fit(X_train)
clust_pred = km.predict(X_test)
\end{pythoncode}

@@

\texttt{Pipeline} and \texttt{FeatureUnion} can be
combined to create complex and nested workflows.
The following snippet illustrates how to create a complex estimator
that computes both linear PCA and kernel PCA features on \texttt{X\_train}
(through a \texttt{FeatureUnion}),
selects the 10 best features in the combination according to an ANOVA test
and feeds those to an $\ell_2$-regularized logistic regression model:
\begin{pythoncode}
fu = FeatureUnion([("pca", PCA()),
                   ("kpca", KernelPCA(kernel="rbf"))])

Pipeline([("feat_union", fu),
          ("feat_sel", SelectKBest(k=10)),
          ("log_reg", LogisticRegression(penalty="l2"))
]).fit(X_train, y_train).predict(X_test)
\end{pythoncode}
